Exposure Consequences - Statistics and Figures

### 2018-01-21 ManuscriptMaterials.Rmd
use York Red as color and allow the correlations on task iteration 1 or 2-5 or both

Here I collect the 'right' statistics and figures for the exposure consequences project.

@@

```{r fig.width=10, fig.height=4}
plotReachAftereffects()
```

@@

```{r fig.width=10, fig.height=4}
plotLocalization()
```

@@

@@

## Correlations

@@

>>>>

This is a collection of statistics and figures for the manuscript on the exposure consequences project.

@@

```{r fig.width=7.5, fig.height=4}
plotReachAftereffects()
```

_For Panel B: We're not really interested in reach aftereffects per se. One focus of this plot/analyses could be the motor changes evoked by the two different types of training. Then it would make more sense to use the initial rotated no-cursor block (I think this is what it does now), as they are directly evoked by the training, and could reflect the motor changes themselves better. Or do we want to focus on the motor changes that are present throughout localization? In that case it makes more sense to use the four later tasks, as they decay stops fairly quickly, so these might be said to better reflect the motor changes that are present throughout the localization tasks. We could also use some average... I can see it many different ways, just want to have a clear strategy here._

@@

```{r fig.width=7.5, fig.height=4}
plotLocalization()
```

@@

_I'm not sure if we should use the initial reach aftereffects here, or the four later blocks. Unfortunately, it does matter for the results, but I don't want to choose with hindsight._

@@

## Pearons Correlations

@@

## Linear regression models
